InteroceptionScale (study 2) - Data Analysis

### 2025-06-23 study1/analysis/1_cleaning.qmd
bits and bobs

@@

Mahalanobis distance [@demaesschalck2000] is commonly used to detect multivariate outliers, which are data points with unusual combinations of scores on two or more variables [@filzmoser2016]. This distance is calculated relative to the centroid—a central point where the means of all variables intersect—with larger distances indicating greater deviation from the center.

This measure takes into account correlations within the dataset, which is especially useful when trying to refine and validate a questionnaire with overlapping items.

>>>>

The initial sample included `r report::report_participants(df, age = "Age", sex = NA, gender = "Gender")`.

@@

### 2025-06-23 study1/analysis/2_analysis.qmd
bits and bobs

---
title: "InteroceptionScale - Data Analysis"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: false
    toc: true
execute: 
  cache: true
---

@@

@@

p_sim <- rez |>
  pivot_longer(-c("Comparison", "Sample", "Iteration")) |>
  filter(str_detect(name, "d_") & str_detect(Comparison, "Facet")) |>
  filter(Sample == "Random") |>
  ggplot(aes(x=value, y=name)) +
  ggdist::stat_eye(aes(fill = after_stat(x < 0))) +
  geom_vline(xintercept=0, linetype="dashed") +
  labs(x="Similarity Difference", y="Indices of pattern difference",
       title="To which matrix is the random one more similar?",
       fill="More similar to") +
  theme_minimal() +
  scale_fill_manual(values=c("TRUE"="#2196F3", "FALSE"="#4CAF50"), labels = c("By modality", "By facet"))

@@

p1 / (p2 | p_sim | p3) +
  patchwork::plot_layout(heights=c(3, 1)) +
  patchwork::plot_annotation(
    title="Effect of Item-presentation Grouping",
    theme = theme(plot.title = element_text(hjust = 0.5, face="bold")))
```

@@

>>>>

---
title: "InteroceptionScale - Study 1: Data Analysis"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: false
    toc: true
execute: 
  cache: true
---

## Original Items

```{r}
#| message: false
#| warning: false
#| out-width: "100%"

knitr::include_graphics("figures/table_originalitems.png")
```

@@

rez[rez$Comparison ==  "Random vs. Facet",  "d_PSI"] |> 
  pd()
rez[rez$Comparison ==  "Random vs. Facet" & rez$Sample == "Random",  "d_PSI"] |> 
  pd()

rez |> 
  summarize(PSI = mean(PSI),
            p_PSI = as.numeric(bayestestR::pd(d_PSI, as_p=TRUE)),
            RVadj = mean(RVadj),
            p_RVadj = as.numeric(bayestestR::pd(d_RVadj, as_p=TRUE)),
            SMI = mean(SMI),
            p_SMI = as.numeric(bayestestR::pd(d_SMI, as_p=TRUE)),
            .by = "Comparison")
```

@@

p_sim <- rez |>
  pivot_longer(-c("Comparison", "Sample", "Iteration")) |>
  filter(str_detect(name, "d_") & str_detect(Comparison, "Facet")) |>
  filter(Sample == "Random") |>
  mutate(name = str_remove(name, "d_"), value = -value) |> # Reverse score for figure aesthetics
  ggplot(aes(x=value, y=name)) +
  ggdist::stat_eye(aes(fill = after_stat(x < 0))) +
  geom_vline(xintercept=0, linetype="dashed") +
  labs(x="Similarity Difference", y="Indices of pattern difference",
       title="Which matrix is the above more similar to?",
       fill="More similar to") +
  theme_minimal() +
  scale_fill_manual(values=c("TRUE"="#4CAF50", "FALSE"="#2196F3"), 
                    labels = c("By facet", "By modality"),
                    guide = guide_legend(reverse = TRUE)) +
  theme(plot.title = element_text(hjust = 0.5, face="italic"))

@@

fig1 <- p1 / (p3 | p_sim | p2) +
  patchwork::plot_layout(heights=c(3, 1)) +
  patchwork::plot_annotation(
    title="Effect of Item Grouping",
    theme = theme(plot.title = element_text(hjust = 0.5, face="bold")))
fig1

ggsave("figures/fig1_correlations.png", fig1, scale = 1.25, width=2100, height=2100, dpi=300, units = "px")
```

@@

### Distributions

```{r}
items |> 
  bayestestR::estimate_density(method="kernSmooth") |> 
  separate(Parameter, into=c("Facet", "Modality", "Item"), sep="_") |>
  ggplot(aes(x=x, y=y)) +
  geom_line(aes(color=Facet, group=interaction(Facet, Item)), linewidth=1, alpha=0.9) +
  facet_wrap(~Modality) +
  theme_minimal() +
  scale_color_material_d(palette = "rainbow") +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank())
```

### 2025-06-23 study2/analysis/1_cleaning.qmd
bits and bobs

```{r}
# Compute distance
dfoutlier <- performance::check_outliers(select(df, contains("MAIA_")), 
                                         method=c("optics"),
                                         threshold=list(optics=2.5, optics_xi=0.03)) |> 
  as.data.frame() |> 
  mutate(Participant = fct_reorder(df$Participant, Distance_OPTICS),
         Outlier_AttentionCheck = ifelse(Participant %in% outliers$attentionchecks, 1, 0),
         Outlier_Duration = ifelse(Participant %in% outliers$duration, 1, 0),
         Outlier = ifelse(Outlier_AttentionCheck == 1, "Failed Attention Checks", "Passed"),
         Outlier = ifelse(Outlier == "Passed" & Outlier_Duration == 1, "Duration", Outlier))

outliers$distance <- as.character(dfoutlier[dfoutlier$Distance_OPTICS < 3, "Participant"])
outliers$distance <- outliers$distance[!outliers$distance %in% c(outliers$attentionchecks, outliers$duration)]

p1 <- dfoutlier |> 
  ggplot(aes(x=Participant, y=Distance_OPTICS)) +
  geom_bar(aes(fill=Outlier), stat="identity") +
  geom_hline(yintercept = 3, linetype="dashed", color="red") +
  labs(fill = "Status") +
  scale_fill_manual(values=c("Duration" = "purple", "Failed Attention Checks"="red", "Passed"="grey")) +
  theme_minimal() +
  theme(axis.text.x = element_blank(),
        panel.grid.major.x = element_blank())

@@

p2 <- estimate_relation(m, length=30) |> 
  ggplot(aes(x=Distance_OPTICS, y=Predicted)) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high), alpha=0.2) +
  geom_line() +
  geom_vline(xintercept=3, linetype="dashed", color="red") +
  theme_minimal()

>>>>

```{r}
# Compute distance
dfoutlier <- performance::check_outliers(select(df, contains("MAIA_")), 
                                         method=c("optics"),
                                         threshold=list(optics=2.5, optics_xi=0.01)) |> 
  as.data.frame() |> 
  mutate(Participant = fct_reorder(df$Participant, Distance_OPTICS),
         Outlier_AttentionCheck = ifelse(Participant %in% outliers$attentionchecks, 1, 0),
         Outlier_Duration = ifelse(Participant %in% outliers$duration, 1, 0),
         Outlier = ifelse(Outlier_AttentionCheck == 1, "Failed Attention Checks", "Passed"),
         Outlier = ifelse(Outlier == "Passed" & Outlier_Duration == 1, "Duration", Outlier))

outliers$distance <- as.character(dfoutlier[dfoutlier$Distance_OPTICS < 3.3, "Participant"])
outliers$distance <- outliers$distance[!outliers$distance %in% c(outliers$attentionchecks, outliers$duration)]

p1 <- dfoutlier |> 
  ggplot(aes(x=Participant, y=Distance_OPTICS)) +
  geom_bar(aes(fill=Outlier), stat="identity") +
  geom_hline(yintercept = 3.3, linetype="dashed", color="red") +
  labs(fill = "Status") +
  scale_fill_manual(values=c("Duration" = "purple", "Failed Attention Checks"="red", "Passed"="grey")) +
  theme_minimal() +
  theme(axis.text.x = element_blank(),
        panel.grid.major.x = element_blank())

@@

p2 <- estimate_relation(m, length=30) |> 
  ggplot(aes(x=Distance_OPTICS, y=Predicted)) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high), alpha=0.2) +
  geom_line() +
  geom_vline(xintercept=3.3, linetype="dashed", color="red") +
  geom_hline(yintercept=1/3, linetype="dashed", color="black") +
  theme_minimal()

### 2025-06-23 study2/analysis/2_analysis.qmd
bits and bobs

items <- filter(df, !is.na(MINT_Awareness_ExAc_35)) 
names(items) <- str_remove(names(items), "MINT_")

@@

dimensions <- list(
  C08 = "CaCo",       # Cardiorespiratory Confusion
  C01 = "UrIn",       # Urointestinal Inaccuracy
  C02 = "Derm",       # Dermatoception
  C10 = "CaNo",       # Cardiorespiratory Noticing
  C13 = "Sati",       # Satiety Noticing

  C14 = "SexS",       # Sexual Arousal Sensitivity
  C07 = "StaS",       # State Specificity
  C09 = "SexO",       # Sexual Organs Sensitivity
  C03 = "ExAc",       # Expulsion Accuracy
  C06 = "RelA",       # Relaxation Awareness

  C05 = "Resp",       # Respiroception
  C11 = "Card",       # Cardioception
  C12 = "Gast",       # Gastroception
  C04 = "Olfa"       # Olfactory Compensation

  # C04 = "SexA",       # Sexual Arousal Awareness
  # C08 = "UrSe",       # Urointestinal Sensitivity
  # C12 = "Sign",       # Signalling
  # C07 = "SexC"        # Sexual Arousal Changes  
)

@@

rbind(higher, select(lower, -ID)) |>
# rbind(higher, lower) |>
  datawizard::data_relocate("Label", after = "Item") |>
  datawizard::data_rename(names(dimensions), dimensions) |>
  select(-Cluster, -Max) |> 
  mutate(`|` = "") |> 
  gt::gt() |>
  gt::tab_row_group(
    label = "Items",
    rows = 1:(nrow(lower) + nrow(higher))
  ) |>
  gt::tab_row_group(
    label = "Metaclusters",
    rows = 1:nrow(higher)
  ) |>
  gt::data_color(columns=-Item,
                 method = "numeric",
                 palette = c("red", "white", "green"),
                 domain = c(-1, 1)) |>
  gt::tab_style(
    style = gt::cell_text(size="small", style="italic"),
    locations = gt::cells_body(columns="Label", rows=c(4:45))
  ) |>
  gt::tab_style(
    style = list(gt::cell_text(weight="bold"),
                 gt::cell_fill(color = "#F5F5F5")),
    locations = list(
      gt::cells_row_groups(groups = "Items"),
      gt::cells_row_groups(groups = "Metaclusters")
    )
  ) |>
  gt::fmt_number(columns=-Item, decimals=2) |>
  gt::tab_header(
    title = gt::md("**Item Loadings**"),
    subtitle = "Node centrality"
  ) 
```

@@

```{r}
df$MINT_Deficit_CaCo <- rowMeans(select(df, starts_with("MINT_Deficit_CaCo_")), na.rm = TRUE)
df$MINT_Deficit_Urin <- rowMeans(select(df, starts_with("MINT_Deficit_Urin_")), na.rm = TRUE)
# df$MINT_Deficit <- rowMeans(select(df, MINT_Deficit_CaCo, MINT_Deficit_Urin))

df$MINT_Sensitivity_Derm <- rowMeans(select(df, starts_with("MINT_Sensitivity_Derm_")), na.rm = TRUE)
df$MINT_Deficit_Sati <- rowMeans(select(df, starts_with("MINT_Deficit_Sati")), na.rm = TRUE)
df$MINT_Deficit_CaNo <- rowMeans(select(df, starts_with("MINT_Deficit_CaNo")), na.rm = TRUE)
# df$MINT_LackSensitivity <- rowMeans(select(df, MINT_Sensitivity_Derm, MINT_Deficit_Sati, MINT_Deficit_CaNo))

df$MINT_Awareness_SexS <- rowMeans(select(df, starts_with("MINT_Awareness_SexS")), na.rm = TRUE)
df$MINT_Awareness_StaS <- rowMeans(select(df, starts_with("MINT_Awareness_StaS")), na.rm = TRUE)
df$MINT_Awareness_SexO <- rowMeans(select(df, starts_with("MINT_Awareness_SexO")), na.rm = TRUE)
df$MINT_Awareness_ExaC <- rowMeans(select(df, starts_with("MINT_Awareness_ExaC")), na.rm = TRUE)
df$MINT_Awareness_RelA <- rowMeans(select(df, starts_with("MINT_Awareness_RelA")), na.rm = TRUE)
df$MINT_Awareness <- rowMeans(select(df, MINT_Awareness_SexS, MINT_Awareness_StaS, MINT_Awareness_SexO, MINT_Awareness_ExaC, MINT_Awareness_RelA))

df$MINT_Interoception_Card <- rowMeans(select(df, starts_with("MINT_Sensitivity_Card")), na.rm = TRUE)
df$MINT_Interoception_Resp <- rowMeans(select(df, starts_with("MINT_Sensitivity_Resp")), na.rm = TRUE)
df$MINT_Interoception_Gast <- rowMeans(select(df, starts_with("MINT_Sensitivity_Gast")), na.rm = TRUE)
df$MINT_Interoception <- rowMeans(select(df, MINT_Interoception_Card, MINT_Interoception_Resp, MINT_Interoception_Gast))

df$MINT_Deficit_Olfa <- rowMeans(select(df, starts_with("MINT_Deficit_Olfa")), na.rm = TRUE)
# df$MINT_Awareness_UrSe <- rowMeans(select(df, starts_with("MINT_Awareness_UrSe")), na.rm = TRUE)

# df$MINT_Awareness <- rowMeans(select(df, starts_with("MINT_Awareness"), -matches("[[:digit:]]")))

df <- df[names(df)[!grepl("MINT_.*[0-9]$", names(df))]]

minti <- data.frame(
  # MINT_Deficit = df$MINT_Deficit,
  MINT_Awareness = df$MINT_Awareness,
  MINT_Interoception = df$MINT_Interoception
)
```

@@

make_cor(select(df, starts_with("MINT"))) +
  labs(x="", y="", title="Correlation between MINT dimensions") +
  theme(axis.text.x = element_text(angle = 45, hjust=1, 
                                   face=c("bold", "plain", "plain", "plain", "bold", "bold", "plain", "plain",
                                          "plain", "plain", "plain", "plain", "plain", "plain", "plain", "plain",
                                          "plain", "plain")))
```

@@

make_cor <- function(df1, df2) {
  df1 |> 
    correlation::correlation(df2, p_adjust="none") |> 
    correlation::cor_sort() |>
    mutate(label = ifelse(p < .001, paste0(insight::format_value(r)), ""),
           Parameter1 = cleanlabels(Parameter1, qname=FALSE),
           Parameter2 = cleanlabels(Parameter2, qname=TRUE)) |> 
    ggplot(aes(x=Parameter1, y=Parameter2, fill=r)) +
    geom_tile() +
    geom_text(aes(label=label), size=3) +
    scale_fill_gradient2(low="blue", high="red", mid="white", midpoint=0) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust=1),
          legend.position = "none")
}

@@

```{r}
select(df, starts_with("MINT"), starts_with("MAIA"), IAS, BPQ) |> 
  parameters::factor_analysis(n=4, rotation="oblimin") |> 
  plot()
```

```{r}
# library(umap)
# 
# items_intero <- select(df, starts_with("MINT"), -matches("[[:digit:]]"), starts_with("MAIA"), IAS, BPQ)
# rez <- umap::umap(datawizard::data_transpose(items_intero[complete.cases(items_intero),]))
# 
# rez
# as.data.frame(rez$layout) |> 
#   rownames_to_column(var="Variable") |> 
#   separate(Variable, into=c("Questionnaire", "Dimension", "Sub"), fill="right") |> 
#   ggplot(aes(x=V1, y=V2, color=Questionnaire)) +
#   geom_point(size=3) +
#   scale_color_manual(values=colors)
```

@@

  preds <- c()
  for(m in models){
    x <- names(sort(abs(coef(m)[-1]), decreasing=TRUE))
    preds <- c(preds, paste0(cleanlabels(x), collapse = ", "))
  }
  test$Predictors <- preds
  format(test, zap_small = TRUE)
}

@@

  # Full Questionnaires
  m_mint <- lm(as.formula(paste0(outcome, " ~ .")),
              data = select(df, all_of(outcome), starts_with("MINT"), -matches("[[:digit:]]$"))) |> 
    step(direction = "both", trace=0)
  m_minti <- lm(as.formula(paste0(outcome, " ~ .")),
              data = cbind(minti, df[outcome])) |> 
    step(direction = "both", trace=0)
  m_ias <- lm(as.formula(paste0(outcome, " ~ IAS")),
              data = df)
  m_maia <- lm(as.formula(paste0(outcome, " ~ .")),
                data = select(df, all_of(outcome), starts_with("MAIA"))) |> 
    step(direction = "both", trace=0)
  m_maiai <- lm(as.formula(paste0(outcome, " ~ .")),
                data = select(df, all_of(outcome), 
                              starts_with("MAIA"), 
                              -contains("NotWorrying"),
                              -contains("NotDistracting"))) |> 
    step(direction = "both", trace=0)
  m_maiamin <- lm(as.formula(paste0(outcome, " ~ .")),
                data = select(df, all_of(outcome),
                              MAIA_AttentionRegulation, # remove?
                              MAIA_SelfRegulation, # remove?
                              # MAIA_Trusting, # remove?
                              MAIA_BodyListening, 
                              MAIA_EmotionalAwareness,
                              MAIA_Noticing)) |> 
    step(direction = "both", trace=0)
  m_bpq <- lm(as.formula(paste0(outcome, " ~ BPQ")),
                data = df)

  models_full <- list(m_mint=m_mint, m_minti=m_minti, m_maia=m_maia, m_maiai=m_maiai, m_maiamin=m_maiamin, m_ias=m_ias, m_bpq=m_bpq)
  test_all <- table_models(models_full)

>>>>

items <- df |> 
   filter(!is.na(MINT_Awareness_ExAc_35)) |> 
  select(starts_with("MINT_")) 
names(items) <- str_remove(names(items), "MINT_")

@@

dimensions <- list(
  C01 = "SexS",       # Sexual Arousal Sensitivity
  C02 = "SexO",       # Sexual Organs Sensitivity
  C03 = "Derm",       # Dermatoception
  C04 = "StaS",       # State Specificity
  C05 = "Card",       # Cardioception
  C06 = "Sati",       # Satiety Noticing
  C07 = "Gast",       # Gastroception
  C08 = "Olfa",       # Olfactory Compensation
  C09 = "Resp",       # Respiroception
  C10 = "RelA",       # Relaxation Awareness
  C11 = "Urin",       # Urointestinal Inaccuracy
  C12 = "ExAc",       # Expulsion Accuracy
  C13 = "CaCo",       # Cardiorespiratory Confusion
  C14 = "CaNo"        # Cardiorespiratory Noticing
)

@@

rbind(higher, select(lower, -ID)) |>
# rbind(higher, lower) |>
  datawizard::data_relocate("Label", after = "Item") |>
  datawizard::data_rename(names(dimensions), dimensions) |>
  select(-Cluster, -Max) |> 
  mutate(`|` = "") |> 
  gt::gt() |>
  gt::tab_row_group(
    label = "Items",
    rows = 1:(nrow(lower) + nrow(higher))
  ) |>
  gt::tab_row_group(
    label = "Metaclusters",
    rows = 1:nrow(higher)
  ) |>
  gt::data_color(columns=-Item,
                 method = "numeric",
                 palette = c("red", "white", "green"),
                 domain = c(-1, 1)) |>
  gt::tab_style(
    style = gt::cell_text(size="small", style="italic"),
    locations = gt::cells_body(columns="Label", rows=c(4:45))
  ) |>
  gt::tab_style(
    style = list(gt::cell_text(weight="bold"),
                 gt::cell_fill(color = "#F5F5F5")),
    locations = list(
      gt::cells_row_groups(groups = "Items"),
      gt::cells_row_groups(groups = "Metaclusters")
    )
  ) |>
  gt::fmt_number(columns=-Item, decimals=2) |>
  gt::tab_header(
    title = gt::md("**Item Loadings**"),
    subtitle = "Node centrality"
  ) |> 
  # Metacluster 1
  gt::tab_style(
    style = gt::cell_fill(color = "#B39DDB"),
    locations = list(
      gt::cells_column_labels(columns = 3),
      gt::cells_body(columns="Item", rows=c(4:6))
    )
  ) |>
  gt::tab_style(
    style = gt::cell_fill(color = "#9FA8DA"),
    locations = list(
      gt::cells_column_labels(columns = 4),
      gt::cells_body(columns="Item", rows=c(7:9))
    )
  ) |>
  gt::tab_style(
    style = gt::cell_fill(color = "#90CAF9"),
    locations = list(
      gt::cells_column_labels(columns = 5),
      gt::cells_body(columns="Item", rows=c(1, 10:12))
    )
  ) |>
  gt::tab_style(
    style = gt::cell_fill(color = "#81D4FA"),
    locations = list(
      gt::cells_column_labels(columns = 6),
      gt::cells_body(columns="Item", rows=c(13:15))
    )
  ) |>
  gt::tab_style(
    style = gt::cell_fill(color = "#80DEEA"),
    locations = list(
      gt::cells_column_labels(columns = 7),
      gt::cells_body(columns="Item", rows=c(16:18))
    )
  ) 
```

@@

```{r}
df$MINT_Awareness_SexS <- rowMeans(select(df, starts_with("MINT_Awareness_SexS")), na.rm = TRUE)
df$MINT_Awareness_StaS <- rowMeans(select(df, starts_with("MINT_Awareness_StaS")), na.rm = TRUE)
df$MINT_Awareness_SexO <- rowMeans(select(df, starts_with("MINT_Awareness_SexO")), na.rm = TRUE)
df$MINT_Awareness_ExaC <- rowMeans(select(df, starts_with("MINT_Awareness_ExaC")), na.rm = TRUE)
df$MINT_Awareness_RelA <- rowMeans(select(df, starts_with("MINT_Awareness_RelA")), na.rm = TRUE)

df$MINT_Deficit_CaCo <- rowMeans(select(df, starts_with("MINT_Deficit_CaCo_")), na.rm = TRUE)
df$MINT_Deficit_Urin <- rowMeans(select(df, starts_with("MINT_Deficit_Urin_")), na.rm = TRUE)
df$MINT_Deficit_Sati <- rowMeans(select(df, starts_with("MINT_Deficit_Sati")), na.rm = TRUE)
df$MINT_Deficit_Derm <- rowMeans(select(df, starts_with("MINT_Sensitivity_Derm_")), na.rm = TRUE)
df$MINT_Deficit_CaNo <- rowMeans(select(df, starts_with("MINT_Deficit_CaNo")), na.rm = TRUE)
df$MINT_Deficit_Olfa <- rowMeans(select(df, starts_with("MINT_Deficit_Olfa")), na.rm = TRUE)

df$MINT_Interoception_Resp <- rowMeans(select(df, starts_with("MINT_Sensitivity_Resp")), na.rm = TRUE)
df$MINT_Interoception_Card <- rowMeans(select(df, starts_with("MINT_Sensitivity_Card")), na.rm = TRUE)
df$MINT_Interoception_Gast <- rowMeans(select(df, starts_with("MINT_Sensitivity_Gast")), na.rm = TRUE)

df <- df[names(df)[!grepl("MINT_.*[0-9]$", names(df))]]
# df$MINT_Awareness <- rowMeans(select(df, MINT_Awareness_SexS, MINT_Awareness_StaS, 
#                                      MINT_Awareness_SexO, MINT_Awareness_ExaC, MINT_Awareness_RelA))
# df$MINT_Deficit <- rowMeans(select(df, MINT_Deficit_CaCo, MINT_Deficit_Urin, 
#                                    MINT_Deficit_CaNo, MINT_Deficit_Sati, MINT_Sensitivity_Derm))
# df$MINT_Interoception <- rowMeans(select(df, MINT_Interoception_Card, MINT_Interoception_Resp, 
#                                          MINT_Interoception_Gast))
# 
# 
# minti <- data.frame(
#   MINT_Deficit = df$MINT_Deficit,
#   MINT_Awareness = df$MINT_Awareness,
#   MINT_Interoception = df$MINT_Interoception
# )
```

@@

make_cor(select(df, starts_with("MINT"))) +
  labs(x="", y="", title="Correlation between MINT dimensions") 
  # theme(axis.text.x = element_text(angle = 45, hjust=1, 
  #                                  face=c("bold", "plain", "plain", "plain", "bold", "bold", "plain", "plain",
  #                                         "plain", "plain", "plain", "plain", "plain", "plain", "plain", "plain",
  #                                         "plain", "plain")))
```

### Short Version

#### Unicity

```{r}
#| fig-width: 12
#| fig-height: 14

mintg <- data.frame(
  MINT_Awareness = rowMeans(select(df, MINT_Awareness_SexS, MINT_Awareness_StaS, MINT_Awareness_SexO, 
                                   MINT_Awareness_ExaC, MINT_Awareness_RelA)),
  MINT_Deficit = rowMeans(select(df, MINT_Deficit_CaCo, MINT_Deficit_Urin, MINT_Deficit_CaNo, 
                                 MINT_Deficit_Sati, MINT_Deficit_Derm, MINT_Deficit_Olfa)),
  MINT_Interoception = rowMeans(select(df, MINT_Interoception_Card, MINT_Interoception_Resp,
                                       MINT_Interoception_Gast))
)

mintmin <- data.frame(
  MINT_Deficit = rowMeans(select(df, MINT_Deficit_CaCo, MINT_Deficit_Urin, MINT_Deficit_Sati)),
  MINT_Awareness = rowMeans(select(df, MINT_Awareness_RelA, MINT_Awareness_ExaC, MINT_Awareness_StaS)),
  MINT_Interoception = rowMeans(select(df, MINT_Interoception_Card, MINT_Interoception_Resp, MINT_Interoception_Gast))
)

mint6 <- data.frame(
  MINT_Sexs = df$MINT_Awareness_SexS,
  MINT_Derm = df$MINT_Deficit_Derm,
  MINT_Olfa = df$MINT_Deficit_Olfa,
  MINT_Deficit = rowMeans(select(df, MINT_Deficit_CaCo, MINT_Deficit_Urin, MINT_Deficit_Sati)),
  MINT_Awareness = rowMeans(select(df, MINT_Awareness_RelA, MINT_Awareness_ExaC, MINT_Awareness_StaS)),
  MINT_Interoception = rowMeans(select(df, MINT_Interoception_Card, MINT_Interoception_Resp, MINT_Interoception_Gast))
)

# fa <- parameters::factor_analysis(features, n = 3, rotation = "oblimin", sort = TRUE) 
# plot(fa)  
# 
# fa |> 
#   select(Variable, Uniqueness) |> 
#   arrange(desc(Uniqueness))
```

@@

@@

Most correlated dimensions:
- IAS: ExAc
- Trusting: RelA
- Noticing: Resp
- Emotional Awareness; Resp
- Body Listening: Gast
- SelfRegulation: RelA
- AttentionRegulation: RelA
- BPQ: Card

```{r}
# library(umap)
# 
# items_intero <- select(df, starts_with("MINT"), -matches("[[:digit:]]"), starts_with("MAIA"), IAS, BPQ)
# rez <- umap::umap(t(items_intero[complete.cases(items_intero),]))
# 
# rez
# as.data.frame(rez$layout) |>
#   rownames_to_column(var="Variable") |>
#   separate(Variable, into=c("Questionnaire", "Dimension", "Sub"), fill="right") |>
#   ggplot(aes(x=V1, y=V2, color=Questionnaire)) +
#   geom_point(size=3) +
#   scale_color_manual(values=colors)
```

@@

  preds <- c()
  for(m in models){
    x <- names(sort(abs(coef(m)[-1]), decreasing=TRUE))
    preds <- c(preds, paste0(cleanlabels(x), collapse = ", "))
  }
  # test$Predictors <- preds
  format(test, zap_small = TRUE)
}

@@

  # Full Questionnaires
  m_mint <- lm(as.formula(paste0(outcome, " ~ .")),
              data = select(df, all_of(outcome), starts_with("MINT"), -matches("[[:digit:]]$"))) # |> 
    # step(direction = "both", trace=0)
  m_mintg <- lm(as.formula(paste0(outcome, " ~ .")),
              data = cbind(mintg, df[outcome])) # |> 
    # step(direction = "both", trace=0)
  m_mintmin <- lm(as.formula(paste0(outcome, " ~ .")),
              data = cbind(mintmin, df[outcome])) # |> 
    # step(direction = "both", trace=0)
  m_mint6 <- lm(as.formula(paste0(outcome, " ~ .")),
              data = cbind(mint6, df[outcome])) # |> 
    # step(direction = "both", trace=0)
  m_ias <- lm(as.formula(paste0(outcome, " ~ IAS")),
              data = df)
  m_maia <- lm(as.formula(paste0(outcome, " ~ .")),
                data = select(df, all_of(outcome), starts_with("MAIA"))) # |> 
    # step(direction = "both", trace=0)
  m_maiai <- lm(as.formula(paste0(outcome, " ~ .")),
                data = select(df, all_of(outcome), 
                              starts_with("MAIA"), 
                              -contains("NotWorrying"),
                              -contains("NotDistracting"))) # |> 
    # step(direction = "both", trace=0)
  m_maiamin <- lm(as.formula(paste0(outcome, " ~ .")),
                data = select(df, all_of(outcome),
                              # MAIA_AttentionRegulation, # remove?
                              # MAIA_SelfRegulation, # remove?
                              # MAIA_Trusting, # remove?
                              MAIA_BodyListening, 
                              MAIA_EmotionalAwareness,
                              MAIA_Noticing)) # s|> 
    # step(direction = "both", trace=0)
  m_bpq <- lm(as.formula(paste0(outcome, " ~ BPQ")),
                data = df)

  models_full <- list(m_mint=m_mint, m_mintg=m_mintg, m_mintmin=m_mintmin, m_mint6=m_mint6, m_maia=m_maia, 
                      m_maiai=m_maiai, m_maiamin=m_maiamin, m_ias=m_ias, m_bpq=m_bpq)
  test_all <- table_models(models_full)
